Ms 1

### 2017-10-30 ms1/ms1_display.Rmd
display: small fixes

Inappropriate prescribing changed by `r rr2pct(d_c * d_f)`% (95% CI `r rr2pct(d_c_lo * d_f_lo)` -- `r rr2pct(d_c_hi * d_f_hi)`). Appropriate prescribing changed by `r rr2pct((1.0 - d_f * f_i) / (1.0 - f_i) * d_c)`% (95% CI `r rr2pct((1.0 - d_f_hi * f_i) / (1.0 - f_i) * d_c_lo)` -- `r rr2pct((1.0 - d_f_lo * f_i) / (1.0 - f_i) * d_c_hi)`).

@@

adjusted_change_levels = adjusted_changes %>%
  filter(antibiotic != 'overall') %$%
  { c('overall', 'overall_app', 'overall_inapp', antibiotic) } %>%
  rev

@@

adjusted_changes %>%
  bind_rows(inapprop_changes) %>%
  mutate(antibiotic=as.character(antibiotic)) %>%
  mutate(antibiotic=factor(antibiotic, levels=adjusted_change_levels)) %>%
  ggplot(aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_bar(stat='identity', fill=NA, color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in consumption 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

The bars show the adjusted change in consumption. Black circles show unadjusted change in consumption. Blue shows the adjusted change in inappropriate prescribing.

@@

```{r adjusted_changes_table}
adjusted_changes %>% arrange(desc(antibiotic)) %>% kable

>>>>

@@

adjusted_change_levels = adjusted_changes %>%
  filter(antibiotic != 'overall') %$%
  { c('overall', 'overall_app', 'overall_inapp', antibiotic) }

@@

adjusted_changes %>%
  bind_rows(inapprop_changes) %>%
  mutate(antibiotic=as.character(antibiotic)) %>%
  mutate(antibiotic=factor(antibiotic, levels=rev(adjusted_change_levels))) %>%
  ggplot(aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in consumption 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

The bars show the adjusted change in consumption.

@@

```{r adjusted_changes_table}
adjusted_changes %>%
  bind_rows(inapprop_changes) %>%
  mutate(antibiotic=factor(antibiotic, levels=adjusted_change_levels)) %>%
  arrange(antibiotic) %>%
  kable
